---
author: "PJL"
date: "`r Sys.Date()`"
output: html_document
---

```{r, echo = FALSE, eval=TRUE, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
library(tm)
library(wordcloud)
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library(rvest)
library(stringr)
library(dplyr)
library(purrr)
library(data.table)
library(magrittr)
library(tidyverse)
library(caret)
library(pROC)
library(mlbench)
library(GGally)
library(data.table)
library(dplyr)
library(class)
library(gmodels)
library(ROCR)
#options(scipen =99)
```





# original
# scrape
# match
# compare1
# compare2
# compare3
# model1
# model2






## original code that generated the data/model for ASRS paper
```{r, eval = TRUE, echo = FALSE, message=FALSE, warning=FALSE}

##################################################
#
#
#   Building a classification model for providers performing 67028
#
###################################################


## read eye data
## read in new data different from arvo to retain some vars
## create new vars to calculate total cost per patient per npi
#dd = data.table(readRDS("~/Dropbox/cms/allData/cmseyeAll.rds"))

# 
# unique(datax$drugstatus)
# me = dd[lname =="LEE" & fname =="PAUL" & city=="WILLIAMSVILLE"]
#  1568536043
# #me = data3[npi =="1568536043"]
#me = datax[lname =="LEE" & fname =="PAUL" & city=="WILLIAMSVILLE"]

# me$costPerProc = me$srvccnt * me$avgpmt # total cost per procedure
# 
# drug = datax[,(count = length(npi)), by = .(drugstatus)]
# #N 584388			
# #Y	17578	




###########################
#  read data and create datasets with and without drugs
############################

datax = readRDS("~/Dropbox/cms/arvo16/eyeDataWithDemoPopProfileCreatedDec316.rds")


data = datax[year==2014,.(npi, drugstatus,credentials, gender, city, zip, state, providertype, medicareparticipation, code, description, srvccnt, uniquebene, avgpmt, year, medicalschoolname, numberofgrouppracticemembers, participatinginerx, participatinginpqrs, participatinginehr, population, tpp, leveltpp = tpp, yearSinceGrad)]


#dataND = datax[drugstatus =="N"] # remove partD


#####################
# add vars for data with and without drugs
#####################

# with drugs

data$costPerProc = data$srvccnt * data$avgpmt 

data1  = data[, totalPatients := sum(uniquebene), by = .(npi)] 
data2 = data1[, totalPmt := sum(costPerProc), by =. (npi)]
data3 = data2[, pmtPerPatient := totalPmt/totalPatients, by =. (npi)] #prob underestimates since 1 patient can be counted multiple times


#### no drug calcs

dataND = data3[drugstatus =="N"] # remove partD

dataND$costPerProc1 = dataND$srvccnt * dataND$avgpmt 
dataND1  = dataND[, totalPatientsND := sum(uniquebene), by = .(npi)] 
dataND2 = dataND1[, totalPmtND := sum(costPerProc1), by =. (npi)]
dataND3= dataND2[, pmtPerPatientND := totalPmtND/totalPatients, by =. (npi)]

nrow(dataND3)
nrow(data3)



dataToJoin1 = dataND3[,.(npi, totalPmtND, pmtPerPatientND)] # these are the fields that are different - other vars the same
dataToJoin = dataToJoin1[!duplicated(npi)]
nrow(dataToJoin1) #584388
nrow(dataToJoin1) #15009
length(unique(dataToJoin1$npi)) #15009

dataJoined = left_join(data, dataToJoin, by = "npi") #2464
nrow(dataJoined) #203775
nrow(data) #203775
length(unique(dataJoined$npi)) #14635
length(unique(data$npi)) #14635



data = dataJoined 
data$pmtPerPatientND1 = data$totalPmt/totalPatients

####################################
## data saved for tulane talk to compare against asrs membership 5/17/17
####################################

saveRDS(data3, "~/Desktop/projects/asrs17/cmsData14Enhanced.rds")

saveRDS(dataND3, "~/Desktop/projects/asrs17/cmsData14EnhancedND.rds")




#############################
# define functional retinal specialists
# need to perform injx, fa, prp, focal
#############################


##################
#  define codes needed to be retina specialist
##################

codes =c("67028","92235","67228","67210","67145")

codesNames = c("injection", "Fluorescein Angiogram", "PRP", "Focal Laser", "Barrier Laser" )

codesDetailed = sprintf("%s (%s)", codes, codesNames)


##################
#  define datasets for each code
##################

# with drugs

dataR1 = data3[code == codes[1] & year == 2014 ] #3190
dataR2 = data3[code == codes[2] & year == 2014 ] #2643
dataR3 = data3[code == codes[3] & year == 2014 ] #1351
dataR4 = data3[code == codes[4] & year == 2014 ] #1239



# without drugs

dataR1ND = dataND3[code == "67028" & year == 2014 ] #3190
dataR2ND = dataND3[code == "92235" & year == 2014 ] #2643
dataR3ND = dataND3[code == "67228" & year == 2014 ] #1351
dataR4ND = dataND3[code == "67210" & year == 2014 ] #1239

dataToJoin = dataR4ND[,.(npi, totalPmtND, pmtPerPatientND)] # these are the fields that are different - other vars the same



r1 = inner_join(dataR1, dataR2, by = "npi") #2464
r2 = inner_join(r1, dataR3, by = "npi") #1307
r3 = inner_join(r2, dataR4, by = "npi") #999

length(unique(r1$npi)) #2252
length(unique(r2$npi)) #1180
length(unique(r3$npi)) #841

# this causes only 67028 to show
retina1 = dplyr::select(r2,1:28 ) 



## inner_join b/c left join leavessome npis with ND as NA
#retina = inner_join(retina1, dataToJoin, by = "npi")
#nrow(retina) #999
#length(unique(retina$npi)) #841


# get npi# and pull from cmsx
retinaNpi = retina1$npi
retina = datax[npi %in% retinaNpi]
retina = inner_join(retina, dataToJoin, by = "npi")

nrow(retina) #17777
length(unique(retina$npi)) #841

# prob not needed since changed retina df as above
names(retina) = gsub("[.]x|[.]y", "", names(retina))

retina$levelWithDrug = cume_dist(retina$pmtPerPatient)

retina$levelNoDrug = cume_dist(retina$pmtPerPatientND)



###############
#  retina df = comprehensive with and without drugs as separate cols
###############



#############
#  eval change between ND and drug pmts for pmtsPerPatient by Cume-dist
#############

retina$changeRank = retina$levelWithDrug-retina$levelNoDrug



saveRDS(retina, "~/Desktop/projects/asrs17/retinaByFunctionWithND.rds")


# how does the change in ranking show in hist? normal dist
hist(retina$changeRank, breaks = 40)

change = data.frame(change = retina$changeRank)

change1 = filter(change, change > 0)
change1SD = round(sd(change1$change),3)

change2 = filter(change, change < 0)
change2SD = round(sd(change2$change),3)

changeMean = round(mean(change$change),4)
changeMedian = round(median(change$change),3)
changeMedianSD = round(sd(changeMedian),3)


topWithDrugs = filter(retina, levelWithDrug>.89)
topWithNoDrugs = filter(retina, levelNoDrug>.89)
topList = rbind(topWithDrugs, topWithNoDrugs)

me1 = filter(retina, npi =="1568536043")

names(retina)
nrow(retina)

threshold = 0.89
topDrug = filter(retina, levelWithDrug>threshold)$npi
topNoDrug = filter(retina, levelNoDrug >threshold)$npi

# npis over 0.89 in both topDrug and topNoDrug
overlap = topDrug[topDrug %in% topNoDrug]
 




a = hist(retina$pmtPerPatientND, breaks = 50, main = "Figure B", xlab = "Payment Per Patient", ylab = "Frequency")
b =hist(retina$pmtPerPatient, breaks = 50,main = "Figure A", xlab = "Payment Per Patient", ylab = "Frequency")

# transformed power distribution to normal by log trans
c =hist(log(retina$pmtPerPatientND), breaks = 50)
d = hist(log(retina$pmtPerPatient), breaks = 50)

e = round(mean(retina$pmtPerPatientND),3)
f = round(sd(retina$pmtPerPatientND),3)
g = round(min(retina$pmtPerPatientND),3)
h = round(max(retina$pmtPerPatientND),3)



##########################################
#
#  what codes does the retina dataset contain
#
#########################################

#it contains all of the codes performed by all of the 999 npis whch will include all of their codes
# what volume does that group perform


#######################################
## retina without outliers
#######################################

#boxplot(retina)
retinax = retina
retinax$levelx = cume_dist(retinax$pmtPerPatientND)


retina2 = filter(retinax, levelx < 0.97)
nrow(retina2)

b1 = hist(retina2$pmtPerPatientND,main = "Figure C", xlab = "Payment Per Patient", ylab = "Frequency")

print(c("mean pmtPerPatientND",mean(retina2$pmtPerPatientND)))
print(c("sd",sd(retina2$pmtPerPatientND)))
min(retina2$pmtPerPatientND)
max(retina2$pmtPerPatientND)
sd(retina2$pmtPerPatientND)






###############################
# 6/4/17 for goanimate asrs presentation
# r3 = merger of 4 codes - codes are scattered in diff cols
#    - extract npi and back out from cms dataset for retina
#################################


r3npi = unique(r3$npi)  #841
retinaOnly = data3[npi %in% r3npi ]
#nrow(retinaOnly) 17777
# unique(retinaOnly$npi)  #841 - matches r3

## general population - use data3 (all ophth)
## retina population - use retinaOnly

#histogram for intravitreal injections
data3 = data3[,-5]  # dup var 


######
injx = filter(data3, code =="67028")
injx1 = filter(retinaOnly, code =="67028")

hist(injx$tpp)
hist(injx1$tpp)

######

FA = filter(data3, code =="92235")
FA1 = filter(retinaOnly, code =="92235")

hist(FA$tpp, xlim = c(0,5), breaks = 40)
hist(FA1$tpp, xlim = c(0,5), breaks=20)

hist(FA$srvccnt, xlim = c(1,1000), breaks = 1000)
hist(FA$srvccnt, xlim = c(1,1000), breaks = 1000)


#######
prp = filter(data3, code =="67228")
prp1 = filter(retinaOnly, code =="67228")

hist(prp$tpp, xlim = c(0,2.5), breaks = 40)
hist(prp1$tpp, xlim = c(0,2.5), breaks = 40)

hist(prp$srvccnt, xlim = c(1,400), breaks = 400)
hist(prp$srvccnt, xlim = c(1,400), breaks = 400)


#######
focal = filter(data3, code =="67210")
focal1 = filter(retinaOnly, code =="67210")

hist(focal$tpp, xlim = c(0,2.5), breaks = 20)
hist(focal1$tpp,  xlim = c(0,2.5), breaks = 20)

hist(prp$srvccnt, xlim = c(1,400), breaks = 400)
hist(prp$srvccnt, xlim = c(1,400), breaks = 400)


#######
# separate unique npi to have 1 record per npi
data3ppp = data3[!duplicated(npi)]

retinaOnlyppp = retinaOnly[!duplicated(npi)]

retinaOnlyppp$levelx = cume_dist(retinaOnlyppp$pmtPerPatient)

retinaOnlyppp1 = filter(retinaOnlyppp, levelx<0.97)


hist(data3$pmtPerPatient, breaks = 500, xlim = c(0,1000))
hist(retinaOnlyppp$pmtPerPatient, breaks = 100)






```









## asrs membership scrape and saved data



```{r asrsScrape, eval=FALSE, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}

## asrs membership scrape and saved data

membersx = list();
index =1

for (page in 0:55) #this is how the website is set up
{
asrsURL = sprintf("http://www.asrs.org/find-a-specialist/results/List?page=%s", page)
print(asrsURL)

asrs <- read_html(asrsURL)

#Scrape the website for names and address
#find names - all start with \r\n
#find index of names
#find first and last of the index
#delete other rows

members <- asrs %>% 
  html_nodes(".pages , .directory .mute , #content-primary a") %>%
  html_text() 

# these are extraneous lines
extra = grep("^[0-9]{1,2}$|previous|next|Show|More", members, ignore.case = TRUE)

membersx = c(membersx, members[-extra])
index = index + 1

}

## this is the concat of all the names and addresses
dat = unlist(membersx)

#index of names
record = grep("\r\n[ ]*\r\n", dat)  #all names start like this

#actual names
names = dat[record]
names = str_trim(gsub("\r\n","",names))

## traverse through each index of name and get only first address if exists
namex = list()
locx = list()
data = list()


for (i in 1:length(record))
{
  print(i)
  namex[[i]] = str_trim(gsub("\r\n","",dat[record[i]]))
  
  #if no address, then the next record will be another name
  # get only one record
  
  
  if (i != length(record) & record[i+1]- record[i] == 1)
  {
    locx[[i]] = NA 
  } else
  {
    locx[[i]]  = dat[record[i]+1]
  }
  
  data[[i]] = data.frame(name = names[[i]], location = locx[[i]], stringsAsFactors = FALSE)
}

  datx = do.call(rbind, data)
  
  stateNames = gsub(",","|",toString(state.abb))
  datx$state = str_extract(datx$location, stateNames)

  saveRDS(datx, "~/Desktop/projects/retina/asrsMembersAll.rds")
  
  
## datx = retina members with address in US
  retina = datx[!is.na(datx$state),]
  retina$index = 1:nrow(retina)
  stateNames1 = gsub(",","$|",toString(state.abb))
  
## isolate city  
  retina$city = gsub("[0-9()-,]","",retina$location)
  retina$city = gsub(stateNames1,"", retina$city)
  retina$city = gsub(" - – ","", retina$city)
  
## separate out multiple cities listed in one col
  retina$city = strsplit(retina$city,"&") %>%  map(1) 
  retina$city = gsub(stateNames,"", retina$city)

## some records from other countrie but with same state initials are included 
## find and delete
  others = which(grepl("^ ", retina$city))
  retina = retina[-others,]
  
  
  # this function extracts last n elements from a list - DEFINE LIST AND WHAT POSITION
  last <- function(x, pos) { tail(x, n = pos) }
  
  
  # split by comma to separate title
  x = strsplit(retina$name, ",")    
  retina$title1 = map(x,2) %>% as.character()
  retina$title2 = map(x,3) %>% as.character()
  retina$title3 = map(x,4)%>% as.character()
  retina$title4 = map(x,5)%>% as.character()

 
  
  retina$name1 = map_chr(x,1)
  retina$name1 = gsub("Jr.|Sr.|III","", retina$name1)
  
  
  ### function to eliminate  empty elements from lists
  emptyElement = function(x) {
    x[nchar(x)>0]
  }

  
  # split by space to searate names
  y = strsplit(unlist(retina$name1)," ")
  y = map(y, emptyElement)
  
  retina$lname = unlist(lapply(y, function(x) tail(x, n=1)))
  retina$fname= map_chr(y, 1)
  
  
retina = map_df(retina, function(x) ifelse(x == "NULL", NA, x))

retina = map_df(retina, str_trim)
retina = map_df(retina, toupper)

## match criteria with cms
retina$matchCrit = paste0(retina$fname,"-", retina$lname, "-",retina$city,"-", retina$state)


saveRDS(retina, "~/Desktop/projects/retina/asrsMembersUS.rds")

 

```





##  retinaByFunctionPart2
    - retina specialists who derive 70% of pmts from retina procedures
```{r, echo = FALSE, eval=FALSE, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
codes =c("67028","92235","67228","67210","67145")


## collect retina NPI and extract unique codes
retinaNpi = c("1568536043",'1023069846')
codes = data[npi %in% retinaNpi, .(codes1 = unique(code))]$codes


#remove exam codes which is universal
codes = gsub("99204|99203|92012|92014","",codes)
codes = codes[nchar(codes)>0]



# adds additional calcs
addFields = function(data){
  data$costPerProc = data$srvccnt * data$avgpmt 
  data1  = data[, totalPatients := sum(uniquebene), by = .(npi)] 
  data2 = data1[, totalPmt := sum(costPerProc), by =. (npi)]
  data3 = data2[, pmtPerPatient := totalPmt/totalPatients, by =. (npi)] 
  return(data)
}






# determines if revenue from meds > x% of revenue
# determine if retina specialist
fx1 = function(d){
  u = unique(d$npi)
  r = list();
  s = list();
  for (i in 1:length(u)) {
    q= data.table(filter(d, npi == u[i]))
    
    q$costPerProc = q$srvccnt * q$avgpmt # total cost per procedure
    
    
    q1  = q[, totalPatients := sum(uniquebene)] 
    q2  = q1[, totalPmt := sum(costPerProc), by =. (npi)]
    q3  = q2[, pmtPerPatient := totalPmt/totalPatients, by =. (npi)]
    q4 = q3[code %in% codes]
    retinaTotal = sum(q4$costPerProc)
    allTotal = sum(q3$costPerProc)
    #retinaStatus = ifelse(retinaTotal/allTotal > 0.7, "Y", "N")
    
    r[[i]] = ifelse(retinaTotal/allTotal > 0.5, "Y", "N")
    s[[i]] = c(status = r[[i]], key =u[i])
  }
  t = data.frame(do.call(rbind, s))
  t$val = as.character(t$status)
  t$key = as.character(t$key)
  
  return(t)
}


ans = fx1(data3)

retinaR = filter(ans, status =="Y")  #2097
retinaR1 = data[npi %in% retinaR$key]  #16667
names(retinaR2)
#retinaR2 = addFields(retinaR1)

median(retinaR1$pmtPerPatient)
median(data3$pmtPerPatient)

boxplot(retinaR1$pmtPerPatient)
boxplot(data3$pmtPerPatient)
```




# wordcloud

```{r wordcloud, echo = FALSE, eval=FALSE, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}


examCodes = c("92002", "92004","92014", "92012","92004","92002","99214", "99204", "99213", "99214")

text = data3$code
text = text[!text %in% examCodes]


lords<- Corpus(VectorSource(text))
]
# inspect(lords)
# 
# lords <- tm_map(lords, stripWhitespace)
# 
# lords <- tm_map(lords, tolower)
# 
# #lords <- tm_map(lords, removeWords, stopwords(“english”))
# 
# lords <- tm_map(lords, stemDocument)

wordcloud(lords, scale=c(5,0.5), max.words=100, random.order=FALSE, rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "Dark2"))


#92134 - oct
#92083 - vf
#92020 - gonio
#99214 - EM est office pt
#92012 - est
#92004 - new

```






## where do we fall in the big picture

```{r, echo = FALSE, eval=FALSE, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}

# med school count
dataSolo = data[!duplicated(npi)]  #14635

medSchoolCount = dataSolo[,.(.N), by = .(medicalschoolname)]


# avg yearssince graduation
hist(datax$yearSinceGrad, xlim = c(0,70), breaks = 20)

mean(datax$yearSinceGrad)
median(datax$yearSinceGrad)

# avg yearssince graduation by state
stateAge = datax[,.(avg = mean(yearSinceGrad)),by = .(state)]

# CT, DC, WV = oldest states
# NH, PR, Utah - youngest


# expenditure and patients for each field
cms14 = readRDS("~/Dropbox/cms/allData/cmsAll14.rds")
cms14x = addFields(cms14)

cms14Data = cms14x[,.(totalProv = length(unique(npi)), pts = sum(uniquebene),  totalPmt = sum(totalPmt), pmtPerPt = median(pmtPerPatient)),by = .(providertype)]







```

## questions
- where does ophthalmolgy rank
    - by patients
    - by pmt
    - by providers
    
- how old are ophthalmologists
    - overall
    - by state
    - by county
    - by gender
    - compared to all

- where are ophthalmolgists located?
    - 

- most common codes 
    - ophthalmology
        - with exam codes
        - without exam codes
    - all

- specialists profiles

- did release of data have an impact
    


##  match asrs and cms data


```{r, readCMSx, echo = FALSE, eval=FALSE, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}

######################
# read and prep data
######################


# retinal specialists by membership
asrsx = readRDS("~/Desktop/projects/retina/asrsMembersUS.rds")


# retinal specialists by function
#asrsx1 = readRDS("~/Desktop/projects/retina/retinaListASRS.rds")

# not used in this section
asrsx1 = readRDS("~/Desktop/projects/asrs17/retinaByFunctionWithND.rds")

#cmsx = readRDS("~/Dropbox/cms/arvo16/eyeDataWithDemoPopProfileCreatedDec316.rds")
# same data as read in the first module
cmsx = datax


#cmsx = readRDS("~/Desktop/projects/retina/cmsData14Enhanced.rds")
#cmsx = cmsx[,-5] #duplicated column credentials


# one row per name from cms for easier name comp
#cmsx1 = cmsx %>%  group_by(matchCrit) %>%  mutate(rowNum #= row_number()) %>%  filter(rowNum==1)


## steps to merge cms utilization data with asrs members
#####################
# - create matchCrit
# - inner_join
# - remove matchCrit
# - rbind include df
# - create leftOut df
######################


############################
#   Initial Match
#   initial inner_join between asrsx and cmsx
############################

## match criteria with cms
asrsx$matchCrit = paste0(asrsx$fname,"-", asrsx$lname, "-",asrsx$city,"-", asrsx$state)

cmsx$matchCrit = paste0(cmsx$fname,"-", cmsx$lname, "-",cmsx$city,"-", cmsx$state)


## inner_join
matched1 = inner_join(cmsx, asrsx, by = "matchCrit")
nrow(matched1)
length(unique(matched1$name))


# unmatched
unmatched1 = anti_join(asrsx, matched1, by = "name" )
nrow(unmatched1)

# remove matchCrit column for easier rbind and matching downstream
matched1 = select(matched1, -grep("matchCrit", names(matched1)))

unmatched1 = select(unmatched1, -grep("matchCrit", names(unmatched1)))



########################################
##  second match using second matchCrit using leftOut df
##  test for same last name in state and keep if no other Ophth with same last name
#########################################

# create match criteria
unmatched1$matchCrit = sprintf("%s-%s", unmatched1$lname, unmatched1$state)
cmsx$matchCrit = sprintf("%s-%s", cmsx$lname, cmsx$state)


# inner_join using match criteria
matched2 = dplyr::inner_join(cmsx, unmatched1, by = "matchCrit") 

nrow(matched2)
length(unique(matched2$npi))
ncol(matched2)

##########################
## additional rule
    ##    - select providers where there is only one provider with the same lname in the state if that name is in the asrsx list
##########################
matched2a = matched2 %>% group_by(state.x, lname.x) %>%  mutate(uniqueProv =length(unique(npi)))  %>%  filter(uniqueProv ==1) %>%  select(-uniqueProv)

nrow(matched2a)
length(unique(matched2a$npi))
names(matched2a)


# clean field names for rbind
matched2a = matched2a %>% select(-grep("matchCrit", names(matched2a)))

names(matched2a)


# rbind the newly discovered group to the original asrsx
matchedF2 = rbind(data.frame(matched1) ,data.frame(matched2a))

nrow(matchedF2)
length(unique(matchedF2$npi))


## this is what is still left out
# match by name since its a remnant from the asrsx in both
unmatched2 = anti_join(asrsx,matchedF2, by = c("name"))
nrow(unmatched2) #468

#nrow(unmatched2) + length(unique(matchedF$npi)) #1659
nrow(asrsx) # 1663 - lost 4 records


#####################################
## third test leaving out city since this may be misleading (different lcoations for cities for differnet db)
#####################################

# create matchCrit
cmsx$matchCrit = paste0(cmsx$fname,"-", cmsx$lname, "-", cmsx$state)

unmatched2$matchCrit = paste0(unmatched2$fname,"-", unmatched2$lname, "-", unmatched2$state)

# inner_join
matched3 = inner_join(cmsx, unmatched2, by = "matchCrit") 
nrow(matched3)
length(unique(matched3$npi))  #36

# unmatched3
unmatched3 = anti_join(unmatched2, matched3, by = "name")
nrow(unmatched3)   #432 = nrow(unmatched3) - 36


# remove matchCrit to allow rbind
matched3 = select(matched3, -grep("matchCrit", names(matched3)))


# rbind leftIn df
matchedF3= rbind(data.frame(matchedF2) ,data.frame(matched3))

length(unique(matchedF3$npi)) #1227



######################
saveRDS(matchedF3, "~/Desktop/projects/retina/asrsCmsF.rds")

```




















## compare asrs members in CMS prolfile and implied retina specialists from CMS procedures



```{r,eval=FALSE, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}


## read data

# asrs members
asrs1 = readRDS("~/Desktop/projects/retina/asrsCmsF.rds")

asrs1x = asrs1 %>% group_by(npi) %>% mutate(rank = row_number()) %>% filter(rank==1)


# retina by profile
#asrs2x = readRDS("~/Desktop/projects/retina/retinaListASRS.rds")
asrs2x = readRDS("~/Desktop/projects/asrs17/retinaByFunctionWithND.rds")


# cms enhanced - Ophth only and 2014 only
cmsx = readRDS("~/Desktop/projects/retina/cmsData14Enhanced.rds")
#cmsx = cmsx[,-5] #duplicated column credentials



## calculate cmsx cume_dist

cmsx$tppRank = cume_dist(cmsx$tpp)

cmsx$costperProcRank = cume_dist(cmsx$costPerProc)

cmsx$totalPatientsRank = cume_dist(cmsx$totalPatients)

cmsx$totalPmtRank = cume_dist(cmsx$totalPmt)

cmsx$pmtPerPatientRank = cume_dist(cmsx$pmtPerPatient)






# create comprehensive df from asrs2 that codes more than just 4 codes screened for
npiList = unique(asrs2x$npi) #841

asrs2 = filter(cmsx, npi %in% npiList) # filter asrs npi's from cms

nrow(asrs2) #17777
nrow(asrs2x)#999 
#unique(asrs2$npi)  #841



# the nonintersecting npi's b/w asrs members and retina by fx
asrsDiff = anti_join(asrs1x, asrs2, by = "npi")
#nrow(asrsDiff) #731


#### dataset list
# asrs1   - asrs members list 
# asrs2   - presumeed retinal docs
# cmsx    - cms total from 14



##########################################
## Compare 2 groups
##########################################

# list of codes and srvccnt

codes1 = asrs1 %>% group_by(code, description) %>% summarise(count = n(), tppMean = mean(tpp)) %>%  arrange(-desc(count)) 

codes2 = asrs2 %>% group_by(code, description) %>% summarise(count = n(),tppMean = mean(tpp)) %>%  arrange(-desc(count))

# combo of codes1 and codes2
codesx = inner_join(codes1, codes2, by = "code") %>% select(description.y) 





#################################
#  add asrs membership status
#################################

# members of asrs
npi1x = unique(asrs1x$npi)

# retina by profile
npi2x = unique(asrs2x$npi)

# cms data
cmsy = cmsx

# create new vars - asrs for membership and fx for functional
cmsy$asrs = ifelse(cmsy$npi %in% npi1x, "y", "n")
cmsy$asrs = as.factor(cmsy$asrs)

cmsy$fx = ifelse(cmsy$npi %in% npi2x, "y", "n")
cmsy$fx = as.factor(cmsy$asrs)


# need to merge the ND categories
#
# code goes here
#



cmsRetinaByFx = filter(cmsy, npi %in% npi2x)  #841 unique npi

cmsRetinaByMembership = filter(cmsy, npi %in% npi1x)  #1227 unique npi


# merge retina by fx and membership
cmsRetinaMerged = rbind(cmsRetinaByFx, cmsRetinaByMembership)

#length(unique(cmsRetinaMerged$npi)) #1572

members = filter(cmsRetinaMerged, asrs == "y")
nonMembers = filter(cmsRetinaMerged, asrs == "n")

memberCount = length(unique(members$npi)) #1227
nonMemberCount = length(unique(nonMembers$npi)) #345


## calcualte retinal cume_dist

cmsRetinaMerged$tppAdj = cume_dist(cmsRetinaMerged$tpp)

cmsRetinaMerged$costperProcAdj = cume_dist(cmsRetinaMerged$costPerProc)

cmsRetinaMerged$totalPatientsAdj = cume_dist(cmsRetinaMerged$totalPatients)

cmsRetinaMerged$totalPmtAdj = cume_dist(cmsRetinaMerged$totalPmt)

cmsRetinaMerged$pmtPerPatientAdj = cume_dist(cmsRetinaMerged$pmtPerPatient)

## round all numeric columns 
cmsRetinaMerged[,map_lgl(cmsRetinaMerged, is.numeric)] = round(cmsRetinaMerged[,map_lgl(cmsRetinaMerged, is.numeric)],2)

cmsRetinaFinal = select(cmsRetinaMerged, 1:27, 28,35,29,36,30,37,31,38,32,39,33,34)



################################
#
#  join cmsRetinaFinal and zip data which gives county and pooulation with geo
#
#################################

zip = read_csv("~/Dropbox/cms/zip_code_database.csv")
zip1 = read_csv("~/Dropbox/cms/zipDemoUSCensus.csv") #NYC only

zipList = distinct(select(zip, 1,6,7,10,11,15)) 
zipList$zip = as.character(zipList$zip)

cmsRetinaFinal$zip = substr(cmsRetinaFinal$zip,1,5)
#pg = filter(zipList, county =="Fairfax County")
#sum(pg$estimated_population)

zz = left_join(cmsRetinaFinal, zipList, by = "zip")

zz1 = filter(zz, estimated_population == '0') 

zz1npi = unique(zz1$npi)

#zz2 = filter(zz1, row_num)

zz2 = zz1 %>% group_by(county) %>% slice(1)

dataWithCountyRatio = zz %>% group_by(county) %>%  mutate(provRatio = estimated_population/length(npi), provRatioCume = cume_dist(provRatio), length = length(npi))



#### save data ###

saveRDS(dataWithCountyRatio, "~/Desktop/projects/retina/asrsCmsFWithMembershipStatus.rds")
```



























### Analysis Using Combined Data(membership, functional)

```{r model1, echo = FALSE, eval = TRUE}

data = readRDS("~/Desktop/projects/retina/asrsCmsFWithMembershipStatus.rds")

dataCountyRank = data %>% arrange(provRatioCume)

nrow(data)
length(unique(data$npi))

hist(data$pmtPerPatient)
hist(data$pmtPerPatientRank)
hist(data$pmtPerPatientAdj)





```









# Build model

```{r model2, echo = FALSE, eval = FALSE}
names(cmsy)
cmsz = select(cmsy, 2,4,9,15,23,24,25,26,27,28)
cmsz[,1:9] <- lapply(cmsz[,1:9] , factor)

library(caTools)

set.seed(88)
split <- sample.split(cmsz$asrs, SplitRatio = 0.75)
#get training and test data
train <- subset(cmsz, split == TRUE)
test <- subset(cmsz, split == FALSE)

nrow(train)
nrow(test)
nrow(filter(train, asrs =="y"))#16277
nrow(filter(train, asrs =="n"))  #136554
nrow(filter(test, asrs =="y")) #5426
nrow(filter(test, asrs =="n")) #45518
# 
# # logistic regression
# model <- glm(asrs~.,family=binomial(link='logit'),data=train)


# 
# summary(model)
# predict <- predict(model, type = 'response')
# #confusion matrix
# table(dresstrain$Recommended, predict > 0.5)
# #ROCR Curve
# library(ROCR)
# ROCRpred <- prediction(predict, dresstrain$Recommended)
# ROCRperf <- performance(ROCRpred, 'tpr','fpr')
# plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2,1.7))
# #plot glm
# library(ggplot2)
# ggplot(dresstrain, aes(x=Rating, y=Recommended)) + geom_point() + 
# stat_smooth(method="glm", family="binomial", se=FALSE)


```



```{r model3, eval = FALSE}


##################################################
##################################################
##################################################




dataz = dplyr::select(retina, npi, gender, state,  participatinginerx, participatinginpqrs, participatinginehr, population, yearSinceGrad, levelNoDrug)

dataz$Class = ifelse(dataz$levelNoDrug>0.66, "H","L")
dataz$Class = as.factor(dataz$Class)
dataz1 = dplyr::select(dataz, -npi)

## validation set

set.seed(7)
validationIndex <- createDataPartition(dataz$Class, p=0.80, list=FALSE)
# select 20% of the data for validation
validation <- dataz[-validationIndex,]
# use the remaining 80% of data to training and testing the models
dataset <- data.frame(dataz[validationIndex,])
dataset<-na.omit(dataset)


# logistic regression - notCaret 
dataset1 = dplyr::select(dataset, -c(1,9))
dataset1$gender= as.factor(dataset1$gender)
#dataset1$state= as.factor(dataset1$state)
dataset1$Class = as.factor(dataset$Class)
dataset1$population = dataset1$population/1000
dataset1$levelNoDrug = dataset1$levelNoDrug*100

#dataset2 = dplyr::select(dataset1,-state)
model1 <- glm(Class~.,family=binomial(link='logit'),data=dataset1)



fitted.results <- predict(model,newdata=subset(validation,select=c(2,3,4,5,6,7,8,10)),type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)

misClasificError <- mean(fitted.results != validation$Class)
print(paste('Accuracy',1-misClasificError))


## WA and CA show correlation
stateAvg = dataset %>% group_by(state) %>% summarise(mean =mean(levelNoDrug))

a = group_by(dataset, state)
b = summarise(a, mean(levelNoDrug))

datasetx = data.table(dataset)
stateAvg = datasetx[,.(mean(levelNoDrug)),by = .(state)]



```



# Overview
- create df with cume_dist for pmtPerPatient 
    - with drugs and without drugs
    - pmtPerPatient without drugs
    - pmtPerPatient with drugs

- create df for retina providers
    - criteria: injx, fa, prp, focal need to be performed
    - with drugs and without drugs
    - pmtPerPatient without drugs
    - pmtPerPatient with drugs

- conclusion
    - retina reference data
        - rank pmtPerPatient to all Ophth
            - plot with retina in different color
            - retina providers at the high end
            
```{r}
qplot(carat, price, data = diamonds, colour = color)
```

        - rank pmtPerPatient to retina only
            - plot with retina only

        







- Create a list of retinal practioners by function and membership
    - There are `r memberCount` members
    - There are `r nonMemberCount` practioners who are not ASRS members
    - create variable for ASRS membership and retinal by function (asrs, fx)
    
- Rerank each practioner within the retina cohort
    - tpp, costPerProc, totalPatients, totalPmt, pmtPerPatient  





- datasets were read in from CMS('14) and ASRS
- 1st match criteria
    - fname-lname-city-state
- 2nd match criteria
    - lname-state
    - no other duplicate names in the same state
- 3rd match criteria
    - fname-lname-state
- 4th criteria
    - scrub to make sure core retinal codes present
- Will not catch:
    - moved locations between 2014 and 2016 since the CMS dataset is for 2016
    - academics not billing CMS


